---
title: "Untitled"
author: "Tiffany Hsu"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usethis)
library(janitor)

# new packages
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```


## beepr beeps

Use the function `beep()` in beepr package to make an audio alert when your code is done running. 

```{r, eval = FALSE}
#eval = FALSE will not run the code when you knit

# ceates a vector of values in descending order
for (i in rev(seq(1:99))) {
  
 print(paste(i, "bottles of beer on the wall")) 
}

beep(4)
```

## praise and cowsay

Packages built with a single purpose: to be kind and fun.

```{r}
praise("${Exclamation},
       ${EXCLAMATION} ... ${exclamation}!!!")

praise("Holy ${creating}, Batman - this code is 
       ${ADJECTIVE}!")

```

use `cowsay::say()` to make a character say something to you

use `usethis::use_git()` or `usethis::use_github()` to create a repo from an existing rproj

## use paletteer to access thousands of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  # find the minimum and how many observations to find. here we are finding the 10 lowest pressures
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::miltank")
  
```

One spatial data example

```{r}
vegetation <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

# update theme to theme_minimal
# fill color change based on the vegetation
# color of the line to NA (color = NA)


ggplot(data = vegetation) +
  geom_sf(aes(fill = name),  color = NA) + 
  theme_minimal() +
  scale_fill_paletteer_d("ggthemes::manyeys") + 
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jorndada LTER")
  
```

